\subsection{Coreference resolution}
Definition of the coreference:
\begin{itemize}
	\item a relationship between two words or phrases in which both refer to the same person or thing and one is a linguistic antecedent of the other
\end{itemize}
the coreference occurs when two or more expression inside a text refers to the same object (e.g. "Jessica has sold her phone to Marcus": in this phrase the pronoun "her" refers to "Jessica"). 
This analysis is done to capture every coreferences inside the article scraped from the website, with the help of the external library Stanford CoreNLP, and substitute it with the representation of that expression (e.g. Jessica has sold Jessica's phone to Marcus).
\par 
Basically, the algorithm written for this analysis consists in dividing the text in more phrases splitted by a dot, and for each phrase analyze it with CoreNLP. 
After that it has been used BeautifulSoup to analyze the XML which the external library gives back; to find the representation and the coreferences, there is a tag "coreference" inside the XML. 
Since there is also another tag called "sentences" that contains all the text analyzed, so it has been used for the substitution of the pronoun or other literal expression into the representation text. 
Every time a coreference expression is founded, the algorithm will replace that coreference expression (i.e. pronoun or other literal expression) with the representation of that. 
At the end the entire text is reconstructed from the tag XML "sentences" that contains the string of text replaced.
\par
At the end, we decided to split the entire article into different substrings of 5 phrases to avoid an overload of text passed to the method of coreference, because after some tests of article analysis, it has been founded a lot of errors about the coreference (e.g. replacement of "he" with "Clinton"). 
\par
Example of original and coreferenced content:
\begin{itemize}
	\item Last week, we talked about what the "too-big-to-fail" banks were saying on their earnings calls. Now, investors have to know what these mega-banks are up to, because they're the 800-lb gorillas of the market, but I don't own a single one of those. As I mentioned a couple of weeks ago, I like regional banks, because they offer what I like the most: unreasonably good returns. Naturally, I never miss an earnings call from these guys. Especially on the first earnings call after the biggest tax reform since 1986 has been passed.
	\item Last week , we talked about what the "too-big-to-fail" banks were saying on the "too-big-to-fail" banks's earnings calls . Now , investors have to know what the "too-big-to-fail" banks are up to , because the "too-big-to-fail" banks 're the 800-lb gorillas of the market , but I don't own a single one of those . As I mentioned a couple of weeks ago , I like regional banks , because the "too-big-to-fail " banks offer what I like the most : unreasonably good returns . Naturally , I never miss an earnings call from the "too-big-to-fail" banks . Especially on the first earnings call after the biggest tax reform since 1986 has been passed .
\end{itemize}

\subsubsection{Saving Data}
After the analysis of coreference the new data needs to be saved somewhere. In this project it has been stored on a database. The tables created for all the study of article content are:
\begin{itemize}
	\item articles\_en\_analyzed: this contains the same field of the old table "articles\_en\_full" but with 5 more fields:
	\begin{enumerate}
		\item coref\_content: a field that contains the new article content with the coreference replaced with its representative
		\item lemma\_content: this contains the text article with every word lemmatized (made by using the lemma annotators)
		\item sentiment: a field that can contains "very negative", "negative", "neutral", "positive" or "very positive". This is useful for the sentiment analysis
		\item sentimentNoNeutral: it's the same of the above one, but in this case the "neutral" is ignored (i.e. the "neutral" sentiment returned by a phrase from CoreNLP is ignored)
		\item sentimentSummarized: it's the same of the first sentiment, but with this, it analyzes a summarized text instead of the entire article
	\end{enumerate}
	\item openie\_reports: this table is linked with the article id of the table above, and it contains 5 fields:
	\begin{enumerate}
		\item reportId: the number identification of the openie\_reports (primary key)
		\item articleId: the article id of the table above (it's a foreign key)
		\item subject: it represents the subject inside a literal expression
		\item verb: it represents the action of the subject
		\item object: it represents the object on which the action is taken
	\end{enumerate}
\end{itemize}
In this part of the project, the news articles are read from the table "articles\_en\_full", and then after the analysis of coreference, the news are saved on a new table ,called "articles\_en\_analyzed", with two new field: coref\_content and lemma\_content.

